\documentclass[10pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{xcolor}

% =============================
%       STYLE SETTINGS
% =============================
\titleformat{\section}
  {\large\bfseries\uppercase}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{1.2ex}{0.6ex}
\setlength{\parskip}{3pt}
\definecolor{links}{HTML}{1A0DAB}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black,
  citecolor=black
}

\begin{document}

\sloppy
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch =1em

% =============================
% HEADER (Name Left / Contact Right)
% =============================
\noindent
\begin{minipage}[t]{0.60\textwidth}
    {\LARGE \textbf{Joseph Charland}}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.39\textwidth}\raggedleft
    \textbf{\href{mailto:joseph.d.charland@gmail.com}{joseph.d.charland@gmail.com}\\}
    \textbf{(724) 814‑4010}\\
    \textbf{\href{https://www.linkedin.com/in/joseph-charland/}{linkedin.com/in/joseph-charland}}
    \textbf{\href{https://www.linkedin.com/in/joseph-charland/}{joecharland.dev}}
\end{minipage}

\vspace{0.6cm}

% =============================
% BODY – 70/30 COLUMNS
% =============================
\noindent
\begin{minipage}[t]{0.68\textwidth}

% ---------- LEFT COLUMN ----------
\section*{Experience}
\vspace{0.15cm}
\textbf{BNY,} Pittsburgh: Full Stack Software Engineer \\
Nov 2023 – Present
\vspace{0.15cm}
\begin{itemize}[leftmargin=*, nosep]
  \item Developed and maintained a mission‑critical interest rate web app using Java and Angular.
  \item Built Python automation tools to streamline reconciliation and auditing processes.
  \item Consolidated multi‑stage pipelines into a unified push‑to‑deploy system, reducing release complexity and accelerating delivery cycles.
  \item Implemented a trunk‑based branching model to enhance integration cadence and boost overall development velocity.
  \item Integrated mutation testing to developer CI/CD pipeline
  \item Optimized SQL data models (–90\% resource use / +20\% data retrieval).
  \item Built test‑data auto‑generation tools improving team autonomy and coverage (+65\%).
\end{itemize}
\vspace{0.25cm}

\textbf{PNC Bank,} Remote: Software Engineer\\
April 2022 – November 2023
\vspace{0.15cm}
\begin{itemize}[leftmargin=*, nosep]
  \item Designed an API migration system for 16 M+ records with zero downtime.
  \item Reduced API dependency vulnerabilities by 80\%.
  \item Developed an email one time pass code verification API for secure authentication.
  \item Automated API monitoring and reporting for stakeholder visibility.
\end{itemize}

\vspace{0.25cm}

\textbf{PNC Bank,} Project Manager / Business Systems Analyst\\
November 2021 – April 2022
\vspace{0.15cm}
\begin{itemize}[leftmargin=*, nosep]
  \item Spearheaded enterprise UI development in an agile team.
  \item Designed wireframes and inline validation interfaces.
\end{itemize}

\vspace{0.25cm}

\textbf{PNC Bank,} Change Management\\
August 2020 – November 2021
\vspace{0.15cm}
\begin{itemize}[leftmargin=*, nosep]
  \item Built a Visual Basic Excel Macro for PNC's mortgage appraisal management pipeline cutting turnaround time by 37\%.
\end{itemize}

\vspace{0.5cm}

\section*{Education}
\vspace{0.15cm}
\textbf{Georgia Institute of Technology} \\
Masters of Science in Computer Science, Computer Systems and AI Specialization (Expected May 2027)\\[4pt]
\vspace{0.15cm}
\textbf{University of Pittsburgh} \\
Bachelors of Science in Business Information Systems \& Supply Chain Management (December 2019)\\[4pt]
\vspace{0.15cm}
\textbf{Community College of Allegheny County} \\
Associate of Science in Software Development (December 2022)\\[4pt]

\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}
\RaggedRight  % prevents ugly spacing by disabling full justification

\setlength{\parskip}{0.5em} % reduces vertical gaps between sections

\textbf{Skills}\\
API Design, CI/CD, Agile Methodologies, Engineering Leadership, Strategic Planning, Problem Solving

\vspace{0.5cm}

\textbf{Languages}\\
Python, Java, C, TypeScript, JavaScript, SQL, Bash, Visual Basic

\vspace{0.5cm}

\textbf{Frameworks \& Tools}\\
Spring Boot, FastAPI, Flask, Angular, Jenkins

\vspace{0.5cm}

\textbf{DevOps~\&~Version~Control}\\
Git, Bitbucket, GitLab, Jenkins

\vspace{0.5cm}

\textbf{Database~\&~Monitoring}\\
SQLite3, Splunk, Dynatrace, Logscale

\vspace{0.5cm}

\textbf{Testing~\&~QA}\\
JUnit, Automated Unit Testing, Integration Testing

\end{minipage}

\end{document}


